R for Clinical Study Reports and Submission

### 2021-10-05 tlf-baseline.Rmd

Following [ICH E3
guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize critical demographic and baseline characteristics
of the patients in Section 11.2, Demographic and Other Baseline
Characteristics.

>>>>

Following [ICH E3
guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize critical demographic and baseline characteristics
of participants in Section 11.2, Demographic and Other Baseline
Characteristics.
